% !TEX program = xelatex
\documentclass{resume}

\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{linespacing_fix}
\usepackage{scrextend}

\begin{document}
\renewcommand\headrulewidth{0pt}

\name{Kiva Oyama}

\basicInfo{
  \email{imkiva@islovely.icu} \textperiodcentered\
  \github[imkiva]{https://github.com/imkiva}
}

\section{Education}
\datedsubsection{\textbf{Southwest Jiaotong University}, Chengdu, China}{2019/09 - 2023/06}
  Major in Physics, GPA：3.72/4.00

\section{Work Experience}

\datedsubsection{\textbf{PLCT Lab}, Remote}{2023/07 - present}
\role{full-time}{Compiler Engineer}
\begin{addmargin}[0.8em]{0em}
  \datedsubsection{\textbf{LLVM Compiler Infrastructure}}{\url{https://github.com/ruyisdk/llvm-project}}
  Implementing full-featured \textbf{vector extension} for T-Head RISC-V SoCs in the LLVM compiler.
  \begin{itemize}
    \item Lead to refactor the compiler architecture: coexistence with RISC-V standard vector extension.
    \item Lead to implement the compilation-optimization flow of T-Head vector intrinsic functions.
    \item Contributed to vector-related passes: auto-insertion of vector length registers, vector length deduction, etc.
  \end{itemize}
\end{addmargin}

\datedsubsection{\textbf{PLCT Lab}, Remote}{2020/11 - 2023/07}
\role{intern}{PL Researcher}
\begin{addmargin}[0.8em]{0em}
  \datedsubsection{\textbf{The Aya Theorem Prover}}{\url{https://github.com/aya-prover/aya-dev}}
  A dependently-typed programming language and a proof assistant based on Cubical Type Theory.
  \begin{itemize}
    \item Contributed to theory: implementation of de Morgan Cubical Type Theory.
    \item Contributed to DX: inference of typechecking order, termination checker, generalized operator parser, library system, etc.
    \item Contributed to tooling: language server, pretty-printing framework, IntelliJ and VSCode plugin.
    % \item Contributed to runtime: JVM/GraalVM backend (planned).
  \end{itemize}
\end{addmargin}

% \datedsubsection{\textbf{IntelliJ Plugin for Aya}}{\url{https://github.com/aya-prover/intellij-aya}}
% IntelliJ Platform plugin for the Aya language.
% \begin{itemize}
%   \item It integrates Aya LSP into the plugin: semantic highlighting, rename refactoring, search everywhere, etc.
%   \item Inspections and quick-fixes for common errors reported by Aya compiler.
%   \item Interactive debugger which traces the typechecking of Aya programs.
%   \item Proof search action in SearchEverywhere which finds a definition by its signature.
% \end{itemize}

\section{Personal Projects}
\datedsubsection{\textbf{Valheim Emulator}}{\url{https://github.com/imkiva/valheim}}
A RISC-V 64 bit emulator which is capable of running modern Linux.
\begin{itemize}
  \item Type-safe instructions making decoding safe and correct.
  \item Full emulation trace like persistent data structures for debugging real hardware or differential testing.
  \item Used as the reference implementation when testing LLDB RISC-V Instruction Emulator.
\end{itemize}

\datedsubsection{\textbf{KiVM}}{\url{https://github.com/imkiva/KiVM}}
A Java Virtual Machine designed for embedded platforms, following JVM specification version 8.
\begin{itemize}
  \item Support most of Java 8's new features, such as lambda expressions and streams.
  \item Garbage Collector by applying mixed G1-Copying algorithm.
  \item Standard JNI interfaces and bytecode control flow analysis.
  \item Learned a lot about language runtimes.
\end{itemize}

% \datedsubsection{\textbf{fluorine}}{\url{https://github.com/imkiva/fluorine-rs}}
% STLC with ADT, pattern matching and typeclass.
% \begin{itemize}
%   \item Trait-based (typeclass) operators overloading.
%   \item Generic types with constraints solver.
%   \item Easy-to-use ffi macros.
%   \item Experimental JVM backend when no Rust ffi was used.
% \end{itemize}

\section{Skills}
\begin{itemize}[parsep=0.25ex]
  \item \textbf{Programming Languages}:
    \textbf{multilingual} (not limited to any specific language),
    and especially experienced in Java/Scala/Rust/Haskell,
    comfortable with Kotlin/TypeScript/C++ (in random order).

  % language Java
  \item \textbf{Java/Scala/Kotlin}:
    Know about their frontend: mostly the Java compiler. 
    Know about their backend: HotSpot VM, GC algorithms and JIT compiler.
    Implemented a self made JVM.
  
  % language Rust
  \item \textbf{Rust}:
    Familiar with Rust language features and implementations,
    especially its LLVM backend.

  % language PAs
  \item \textbf{Proof assistants: Aya/Agda/Arend}:
    Participated in the core developemnt of the Aya Prover.
    Especially experienced in type-driven development.
  
  \item \textbf{Tooling}:
    Comfortable with any OS/editors. Once contributed code to IntelliJ IDEA community version.
    Especially experienced in Git and GitHub.
\end{itemize}

\section{Miscellaneous}
\begin{itemize}[parsep=0.25ex]
  \item Language: English - CET6, TOEFL-101, Chinese - native
  \item Open Source Contribution: \url{https://github.com/imkiva}
  \item \textbf{2 kyu} on \href{https://www.codewars.com/users/imkiva} {CodeWars}, primarily in Haskell
  \item Prefer remote work. Programming for interest, powered by love.
\end{itemize}

\end{document}
